Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-06 tex/MesnardoBarba2019.tex
Add ppn and num GPU per node for Poisson benchmark
Add information about the number of MPI processes and the number of GPU devices
used per node for the Poisson benchmark.

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
    \caption{Runtimes to solve a Poisson system on Colonial One and on Microsoft Azure. Benchmark was repeated 5 times and we report the mean runtimes as well as the extrema. Poisson system was solved on Azure using PETSc on \texttt{H16r} nodes and using AmgX on \texttt{NC24r} nodes. On Colonial One, we solved the system with PETSc on \texttt{Short} nodes and with AmgX on \texttt{Ivygpu} nodes. The runs with PETSc solved a Poisson system on a mesh size of 50 million cells (top). With AmgX (bottom left), the base mesh size contains 6.25 million cells and we scale it with the number of nodes. On Azure, we also ran the Poisson benchmark with a finer base mesh size of 25 million cells (bottom right). Runtimes obtained with AmgX were normalized by the number of iterations required to reach a absolute tolerance of $10^{-12}$.}
    \label{fig:poisson_benchmarks}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=8cm]{figures/poisson_time_vs_nodes.pdf}
    \caption{Runtime to solve a Poisson system on Colonial One and on Microsoft Azure. Benchmark was repeated 5 times and we report the mean runtime as well as the extrema. Poisson system was solved on Azure using PETSc on \texttt{H16r} nodes ($16$ processes per node) and using AmgX on \texttt{NC24r} nodes ($12$ processes and $1$ NVIDIA K80 GPU per node). On Colonial One, we solved the system with PETSc on \texttt{Short} nodes ($16$ processes per node) and with AmgX on \texttt{Ivygpu} nodes ($12$ processes and $2$ NVIDIA K20 GPUs per node). The runs with PETSc solved a Poisson system on a mesh size of 50 million cells (top). With AmgX (bottom left), the base mesh size contains 6.25 million cells and we scale it with the number of nodes. On Azure, we also ran the Poisson benchmark with a finer base mesh size of 25 million cells (bottom right). Runtimes obtained with AmgX were normalized by the number of iterations required to reach a absolute tolerance of $10^{-12}$.}
    \label{fig:poisson_benchmarks}
\end{figure}
